---
title: "Unit 1 - 3 Review Starter"
author: "Sata Dience"
date: "February 23, 2023"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites) %>%
  ls()

```
There are 23 rows, and 2 variables. Each row is a location of the minerals.

### Exercise 2

```{r inspect-other-data-frames}
glimpse(location_descriptions) %>% 
  ls()

glimpse(density) %>% 
  ls()

glimpse(solubility_hardness) %>% 
  ls()
```
location_descriptions has 10 rows and 2 variables, each row is a location.

Density has 3 rows and two variables, each row is a mineral.

solubility_hardness has 3 rows and 3 variables, each row is a mineral.

### Exercise 3

The output has 23 rows, which is the same as the sand-minerals data set. 

```{r join-mineral-properties}
sand_mineral_density <- density %>%
  left_join(sites)

sand_mineral_density
```

```{r join-mineral-properties2}
sand_mineral_properties <- solubility_hardness %>%
  left_join(sand_mineral_density)

sand_mineral_properties
```


### Exercise 4

```{r number-of-sand-grains-observed}
sand_mineral_properties %>%
  count(location)
```

```{r bottom-slice}
sand_mineral_properties %>%
  slice(14:23)
```

```{r density}
sand_mineral_properties %>%
  arrange(desc(density)) %>%
  slice(14:23)
```

```{r first-and-last}
sand_mineral_properties %>%
  select(c(1,5)) %>%
  slice(19:23)
```

```{r no-more-hardness}
sand_mineral_properties %>%
  na.omit(hardness) %>%
  arrange(desc(density)) %>%
  slice(1:5)
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
